An Analysis of the Use of Average Centipawn Loss to Detect Cheating in Chess

### 2022-12-02 Manuscript/manuscript.tex
refactored dataset

Over the past few months, the global chess community has been shaken by a very high-profile story regarding Hans Niemann, Magnus Carlsen, and “alleged cheating” in chess. This “cheating accusation” scandal started when Carlsen withdrew from the Sinquefield Cup after losing to nineteen-year-old Niemann in a stunning third round defeat. This was the first time in the then reigning five-time World Chess Champion's career where he withdrew from a major event in progress.

Carlsen didn't immediately state the reason as to why he withdrew at first, though many correctly assumed that he was holding his tongue in making any sort of public accusation to avoid a potential retaliatory lawsuit for slander. It should be noted that Carlsen played Niemann again two weeks later in the Julius Baer Generation Cup, but resigned after his second move, perpetuating rumors of the scandal even further. This has become a matter of significant speculation both inside and outside the chess world given the nature of the situation and the people involved.

@@

% removed faulty methods

>>>>

Over the past few months, the global chess community has been shaken by a very high-profile story regarding Hans Niemann, Magnus Carlsen, and “alleged cheating” in chess. The scandal started when Carlsen, the then reining five-time World Chess Champion, withdrew from the Sinquefield Cup after a stunning upset by then nineteen-year-old Niemann in the tournament’s third round. Carlsen didn’t immediately state the reason as to why he withdrew at first, though many correctly assumed he was holding his tongue in making any sort of public accusation of cheating to avoid any potential retaliatory lawsuit, but it was too late. The public was already running wild with the story, and every armature chess player and data scientist was looking for any indication of foul play given the high-stakes nature of the situation and the people involved.

@@

% refactor dataset before adding back methods
